---
title: "Flex Dashboard Example"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    theme: lumen
    orientation: columns
    vertical_layout: fill
    source_code : embed

---

```{r setup, include=FALSE}
library(flexdashboard)
library(southafricastats)
library(dplyr)
library(tidyr)
library(ggplot2)
library(leaflet)
library(DT)

#head(population_zaf)
totals = population_zaf %>%
  filter(year == 2013) %>%
  select(province,total)

#head(totals)


compare_provinces <- mortality_zaf %>% 
  left_join(totals) %>%
  mutate(rate = deaths /total * 1e3) %>%
  group_by(province, indicator) %>%
  summarise(rate = mean(rate)) %>%
  ungroup %>%
  left_join(totals) %>%
  spread(indicator,rate)

#head(compare_provinces)


selected_df <- reactive({
  subset_df <- compare_provinces[,c(1,2,
                                    which(colnames(compare_provinces) == input$x_axis),
                                    which(colnames(compare_provinces) == input$y_axis))]
  colnames(subset_df) <- c('province','total','x','y')
  subset_df
})

selected_df_indicator <- reactive({
  subset_df <- compare_provinces[,c(1,which(colnames(compare_provinces) == input$indicator))]
  colnames(subset_df) <- c('province','indicator')
  population_zaf %>%
    filter(year == 2013) %>%
    left_join(subset_df) %>%
    mutate(indicator = indicator / sum(indicator, na.rm = TRUE))
  #subset_df
})

scatterplot_df <- reactive({
  subset_df <- compare_provinces[,c(1,2,
                                    which(colnames(compare_provinces) == 'All causes'),
                                    which(colnames(compare_provinces) == input$indicator))]
  colnames(subset_df) <- c('province','total','x','y')
  subset_df
  #subset_df
})

mortality = mortality_zaf %>% filter(indicator != 'All causes' & indicator != 'Other natural causes')
nc = mortality_zaf %>% filter(indicator == 'Other natural causes')


```


Column {.sidebar}
====================================================

The sidebar give us information about the plots, together with buttons that we might use the change the view of the data



```{r}
selectInput(inputId = 'indicator',
            label = 'Choose a cause of death',
            choices = unique(mortality_zaf$indicator),
            selected = 'Diabetes mellitus (E10-E14)')
            

```


Map {data-icon="fa-map-marker"}
====================================================
### Mortality Map

```{r}
renderLeaflet({
  leaflet(selected_df_indicator()) %>%
    addProviderTiles("CartoDB.Positron") %>%
    addCircles(lng = ~longitude,
               lat = ~latitude,
               radius = ~sqrt(indicator) *3e5,
               weight = 2.5,
               color = "magenta",
               popup = ~province)
})
```

Comparing Provinces {data-icon="fa-list"}
============================================

### How does the selected mortality rate compare to the overall mortality rate


```{r}
renderPlot({
  ggplot(scatterplot_df(),
       aes(x, y,
           label = province)) + 
  geom_point(aes(size = total),alpha = 0.8,colour = 'midnightblue') +
  geom_text(vjust = 2.5) +
  theme_minimal()
})
```


Changes in time {data-icon='fa-area-chart'}
===========================================
## How have the number of deaths changed over time

```{r}
renderPlot({
       mortality_zaf %>%
       filter(indicator %in% input$indicator) %>%
       ggplot(aes(year,deaths,colour=province)) + 
       geom_line(alpha = 0.8, size = 1.5) +
       theme_minimal(base_size = 18) +
    labs(x = NULL, y = "Number of Deaths")
})
```


Table {data-icon='fa-table}
===========================
### Check out the data here

```{r}
renderDataTable({
  datatable(mortality_zaf %>%
       filter(indicator %in% input$indicator))
})
```


