---
title: "MQ DB"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(dplyr)
library(tidyr)
library(ggplot2)
library(leaflet)
library(DT)
library(reshape)
load('/mnt/BLACKBURNLAB/QC/Reference/summary/QC_db_sim.RData')
#dim(reduced_data)
#head(reduced_data)
#colnames(reduced_data)
#summary$Peaks.Repeatedly.Sequenced....
boxplot(summary$Peaks_Repeatedly_Sequenced_percentage)
#colnames(summary)[4:21]
#colnames(summary)

raw_list = unique(scans$Raw_file[2:length(scans$Raw_file)])

#d=data.frame(date=(c("2014-02", '2014-03', "2014-09", "2016-03",'2016-11','2017-05')), event=c("Dionex",'new QE',"Aeris", "Dual Column and Annual Service",'0','Service and Relocate'))


scans$shift_TIC = scans$Total_ion_current
scans = transform(scans, shift_TIC = c(NA,shift_TIC[-nrow(scans)]))
scans$TIC_variance = ((scans$Total_ion_current-scans$shift_TIC)/scans$shift_TIC) * 100

#ideal_scans$shift_TIC = ideal_scans$Total_ion_current
#ideal_scans = transform(ideal_scans, shift_TIC = c(NA,shift_TIC[-nrow(ideal_scans)]))
#ideal_scans$TIC_variance = #((ideal_scans$Total_ion_current-ideal_scans$shift_TIC)/ideal_scans$shift_TIC) * 100

plot_height_0 = 300
plot_height_1 = 400
plot_height_2 = 700

```




Column {.sidebar}
====================================================

In the panel RAW, current .raw files selected individually or in groups

```{r}

selectInput(inputId = 'file',
            label = 'Raw file',
            choices = raw_list,
            selected = raw_list,
            multiple = TRUE)
            
```



DB {data-icon="fa-list"}
============================================
Column {data-width=350}
-----------------------------------------------------------------------

Current raw files are ovelayed upon ideal raw files


```{r}

library("RSQLite")

print('Database created with /mnt/BLACKBURNLAB/scripts/QC/QC_summary_db.py from all the Reference samples run in MaxQuant since 2013')

database_path = '/blackburn3/temp/db/Ref_QC.db'

print("Database extracted in R workspace using /mnt/BLACKBURNLAB/QC/Reference/summary/temp/Ref_db_plot.R")

print('/mnt/BLACKBURNLAB/QC/Reference/summary/QC_db.RData')
print("Database tables")
print(alltables)

#summary = dbGetQuery( con,"select * from summary_RAW WHERE Date != ''" ) # upload the table summary as a data frame
#num_list = colnames(summary)[c(3:13)]

#for(col_entry in num_list){
#  summary[,col_entry] = as.numeric(summary[,col_entry])
#}

#summary$Date = as.Date(summary$Date, '%Y-%m-%d')

print("recent = summary$Raw_file[as.Date(summary$Date, '%Y-%m-%d') > as.Date('2017-05-15', '%Y-%m-%d') &  as.Date(summary$Date, '%Y-%m-%d') < as.Date('2017-06-01', '%Y-%m-%d')]")
print(recent)

print("best_ids = summary$Raw_file[summary$Peptide_Sequences > 13000 & summary$Peptide_Sequences < 15000 & summary$Gradient == '70' & summary$Loading == '1000ng']")
print(best_ids)

#print(scans_cmd)
#print(evidence_cmd)
#print('Most Recent')
#print(recent)
#print(summary[,c('Raw_file',"Peptide_Sequences")][summary$Raw_file %in% recent,])
#sliderInput("pep_id", "Peptides Identified", 
#             min=0, max=20000,
#             value=c(10000,20000),
#             step = 1,
#             dragRange = T,
#             width = 1500)

# best_ids = reactive({
#   summary$Raw_file[summary$Peptide_Sequences > 10000 & summary$Gradient == "60"  & summary$Loading == "600ng" & summary$Column == 'C1']
# })
# 
# best = renderTable(summary$Raw_file[summary$Peptide_Sequences > input$pep_id[1] & summary$Gradient == "60"  & summary$Loading == "600ng" & summary$Column == 'C1'])
# best()


#print(summary[,c('Raw_file',"Peptide_Sequences")][summary$Raw_file %in% best_ids,])

 # sliderInput("peps", "Peptides Identified", 
 #            min=0, max=20000,
 #            value=c(10000))

```


RAW {data-icon="fa-list"}
============================================
Column {data-width=350}
-----------------------------------------------------------------------

Current raw files are ovelayed upon ideal raw files


```{r}


scans$Total_ion_current = signif(scans$Total_ion_current,3)
 sliderInput("y_range", "TIC Range", 
             min=1e6, max=1.2e10,
             value=c(0,1e10),
             dragRange = T,
             width = 1500)

raw_list = unique(scans$Raw_file[2:length(scans$Raw_file)])

#selectInput(inputId = 'RAW',
#            label = 'RAW file',
#            choices = raw_list)

 sliderInput("x_range", "Retention Time Range", 
             min=0, max=max(scans$Retention_time,na.rm=TRUE),
             value=c(18,88),
             step = 1,
             dragRange = T,
             width = 1500)


fillCol(height = plot_height_0,
renderPlot({
  ggplot(data = scans[scans$Raw_file %in% input$file,], aes(x=Retention_time,y=Total_ion_current,colour=Raw_file)) +
    geom_line(size = 0.75, alpha = 1) +
    ylim(input$y_range[1],input$y_range[2]) +
    xlim(input$x_range[1],input$x_range[2]) +
    theme(text = element_text(size=25),axis.text.x = element_text(angle = 90, hjust = 1))

    #geom_line(data = scans[scans$Raw_file %in% #raw_list[input$file_range[1]:input$file_range[2]],],

},height = plot_height_0))

```


### TIC Variance
```{r}
fillCol(height = plot_height_0,
renderPlot({
ggplot(data = scans[scans$Raw_file %in% input$file,], aes(x=Retention_time,y=TIC_variance,colour=Raw_file)) +
    geom_line(size = 1, alpha = 1) +
    ylim(-20,20) +
    xlim(input$x_range[1],input$x_range[2]) +
    theme(text = element_text(size=25),axis.text.x = element_text(angle = 90, hjust = 1))
},height = plot_height_0))

```



TIC {data-icon="fa-list"}
============================================
Column {data-width=600}
-----------------------------------------------------------------------



```{r}




r_scans = reactive({
  Retention_time_start = input$x_range[1]
  Retention_time_stop = input$x_range[2]
  reduced_scans = scans[evidence$Retention_time > Retention_time_start & evidence$Retention_time < Retention_time_stop & evidence$Raw_file %in% input$file,]
})
```



```{r}

fillCol(height = plot_height_1,
renderPlot({
ggplot(data = r_scans(), aes(x=Raw_file,y=Total_ion_current,colour=Raw_file)) +
  geom_boxplot(size = 0.75, alpha = 1) +
    ylim(1e8,1e10) +
    theme(text = element_text(size=25),axis.text.x=element_blank(),axis.ticks.x=element_blank())

},height = plot_height_1))


```




```{r}
fillCol(height = plot_height_1,
         renderPlot({
                  ggplot(data = r_scans(), aes(x=Raw_file,y=abs(TIC_variance),colour=Raw_file)) +
                    geom_boxplot(size = 0.75, alpha = 1) +
                    ylim(0,30) +
             theme(text = element_text(size=25),axis.text.x=element_blank(),axis.ticks.x=element_blank())
},height = plot_height_1))


```










MS {data-icon="fa-list"}
============================================
Column {data-width=650}
-----------------------------------------------------------------------

### MS

```{r}

fillCol(height = plot_height_1,
renderPlot({
  #q <- qplot(Date,',column_name,',data=reduced_data,geom=c("boxplot","point"),colour = column_volume)
  ggplot(summary[summary$Raw_file %in% input$file,],
       aes(Date, MS)) +
  geom_point(aes(colour = Raw_file)) +
  theme(text = element_text(size=25),axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(x = NULL, y = NULL)
},height = plot_height_1))

```

### MS/MS

```{r}

fillCol(height = plot_height_1,
renderPlot({
  #print(input$integer)
  #q <- qplot(Date,',column_name,',data=reduced_data,geom=c("boxplot","point"),colour = column_volume)
  ggplot(summary[summary$Raw_file %in% input$file,],
       aes(Date, MS_MS)) +
  geom_point(aes(colour = Raw_file)) +
  theme(text = element_text(size=25),axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(x = NULL, y = NULL)
},height = plot_height_1))
```



Ids {data-icon="fa-list"}
============================================
Column {data-width=350}
-----------------------------------------------------------------------

### log2(MS/MS / MS)

```{r}

fillCol(height = plot_height_1,
renderPlot({
  #q <- qplot(Date,',column_name,',data=reduced_data,geom=c("boxplot","point"),colour = column_volume)
  summary$MS2per = log2(summary$MS_MS/summary$MS)
  ggplot(summary[summary$Raw_file %in% input$file,],
       aes(Date, MS2per)) +
  geom_point(aes(colour = Raw_file)) +
    theme(text = element_text(size=25),axis.text.x = element_text(angle = 90, hjust = 1)) +
    scale_y_continuous(limits = c(0,2)) +
    labs(x = NULL, y = NULL)

},height = plot_height_1))

```

### MS_MS_Identified_percentage

```{r}
fillCol(height = plot_height_1,
renderPlot({
  #q <- qplot(Date,',column_name,',data=reduced_data,geom=c("boxplot","point"),colour = column_volume)
  ggplot(summary[summary$Raw_file %in% input$file,],
       aes(Date, MS_MS_Identified_percentage)) +
  geom_point(aes(colour = Raw_file)) +
    theme(text = element_text(size=25),axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(x = NULL, y = NULL)
},height = plot_height_1))
```



Peptides {data-icon="fa-list"}
============================================
Column {data-width=350}
-----------------------------------------------------------------------

### Peptide_Sequences_Identified

```{r}

fillCol(height = plot_height_1,
renderPlot({
  #q <- qplot(Date,',column_name,',data=reduced_data,geom=c("boxplot","point"),colour = column_volume)
  ggplot(summary[summary$Raw_file %in% input$file,],
       aes(Date, Peptide_Sequences)) +
  geom_point(aes(colour = Raw_file)) +
    theme(text = element_text(size=25),axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(x = NULL, y = NULL)


},height = plot_height_1))

```

### Peaks.Repeatedly.Sequenced....

```{r}
fillCol(height = plot_height_1,
renderPlot({
  #q <- qplot(Date,',column_name,',data=reduced_data,geom=c("boxplot","point"),colour = column_volume)
  ggplot(summary[summary$Raw_file %in% input$file,],
       aes(Date, Peaks_Repeatedly_Sequenced_percentage)) +
  geom_point(aes(colour = Raw_file)) +
    theme(text = element_text(size=25),axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(x = NULL, y = NULL)
},height = plot_height_1))
```



VENN {data-icon="fa-list"}
============================================
Column {data-width=600}
-----------------------------------------------------------------------

### Venn
```{r}
library(VennDiagram)

 #raw_summary <- reactive({summary[summary$Raw_file %in% input$file,]})
selectInput(inputId = 'setA',
            label = 'A',
            choices = raw_list,
            selected = raw_list[1],
            width = 1500,
            multiple = TRUE)

selectInput(inputId = 'setB',
            label = 'B',
            choices = raw_list,
            selected = raw_list[2],
            width = 1500,
            multiple = TRUE)

selectInput(inputId = 'setC',
            label = 'C',
            choices = raw_list,
            selected = raw_list[3],
            width = 1500,
            multiple = TRUE)


#plot triple Venn
fillCol(height = 600,
renderPlot({
  
# setA = unique(evidence$Sequence[evidence$Raw_file == raw_venn[1]])
# setB = unique(evidence$Sequence[evidence$Raw_file == raw_venn[2]])
# setC = unique(evidence$Sequence[evidence$Raw_file == raw_venn[3]])

raw_summary = summary[summary$Raw_file %in% input$file,]
raw_A = summary[summary$Raw_file %in% input$setA,]
raw_B = summary[summary$Raw_file %in% input$setB,]
raw_C = summary[summary$Raw_file %in% input$setC,]
if(dim(raw_summary)[1] >= 2){
  
  raw_venn = raw_summary$Raw_file[c(1:3)]
  
  setA = unique(evidence$Sequence[evidence$Raw_file %in% raw_A$Raw_file])
  setB = unique(evidence$Sequence[evidence$Raw_file %in% raw_B$Raw_file])
  setC = unique(evidence$Sequence[evidence$Raw_file %in% raw_C$Raw_file])
    
  draw.triple.venn(length(setA),
                   length(setB),
                   length(setC),
                   n12 = length(intersect(setA,setB)), #overlap between A & B
                   n23 = length(intersect(setB,setC)), #overlap between B & C
                   n13 = length(intersect(setA,setC)), #overlap between A & C
                   n123 = length(intersect(intersect(setA,setB), intersect(setB,setC))), #overlap between all 3
                   category = c('A', 'B', 'C'),
                   #rotation = 1, #default, indicates clockwise rotation of the sets
                   #reverse = TRUE, #binary: should diagram be mirrored along vertical axis
                   euler.d = TRUE, #binary: draw Euler diagrams (Venns with moveable circles) when conditions are met?
                   scaled = TRUE, #binary: scale circles according to set size? (requires euler.d=T)
                   overrideTriple = 1, #assign any value to re-enable general scaling for three-set Venns (may be visually misleading)
                   lwd = rep(0, 3), #width of circumferences
                   lty = rep("blank", 3), #dash pattern of circumference outline
                   #col = c("cadetblue2","thistle","khaki3"), #colour of circumferences
                   fill = c("#66C2A5","#3288BD","#5E4FA2"), #fill colours (can also specify as rep("colourname",3) or as c("colourname1","colourname2","colourname3"))
                   alpha = rep(0.5, 3), #transparency
                   label.col = rep("black", 7), #area label colour
                   cex = rep(1, 7), #area label size
                   fontface = rep("plain", 7),
                   fontfamily = rep("serif", 7),
                   cat.pos = c(-40, 40, 180), #position (in degrees of circle) of category names
                   cat.dist = c(0.05, 0.05, 0.025), #distance of category names from edges of circle
                   cat.col = rep("black", 3), #colours of cat names
                   cat.cex = rep(1, 3), #size of cat names
                   cat.fontface = rep("plain", 3),
                   cat.fontfamily = rep("serif", 3),
                   cat.just = list(c(0.5, 1), c(0.5, 1), c(0.5, 0)), #horizontal and vertical justification of each category name
                   cat.default.pos = "outer", #default location of category names
                   cat.prompts = FALSE,
                   rotation.degree = 0, #no. degrees to rotate entire diagram
                   rotation.centre = c(0.5, 0.5), #indicates rotation centre
                   ind = TRUE, #binary: first draw diagram, then return gList object?
                   sep.dist = 0.05, #distance between circles if sets mutually exclusive
                   offset = 0,
                   print.mode = c('raw','percent')) #offset from centre if inclusive sets
}


},height = 600))
```


Sequences {data-icon="fa-list"}
============================================
Column {data-width=600}
-----------------------------------------------------------------------

evidence[Retention_time > Retention_time_start & Retention_time < Retention_time_stop & Raw_file in file & Charge >= 2,]
```{r}



sliderInput("seq", "Sequence Range",
             min=0, 200,
             value=c(0,5),
             step = 1,
             dragRange = T,
             width = 1500)

fillCol(height = plot_height_2,
renderPlot({
Retention_time_start = input$x_range[1]
Retention_time_stop = input$x_range[2]

reduced_evidence = evidence[evidence$Retention_time > Retention_time_start & evidence$Retention_time < Retention_time_stop & evidence$Raw_file %in% input$file & evidence$Charge >= 2,]
sequences = reduced_evidence$Sequence
#length(sequences)

# arrange sequences with those found most often at the top
# sequences seem to be present multiple times per sample : need to work out why
seq_num = table(sequences)
head(seq_num)
seq_num = seq_num[rev(order(seq_num))]
head(seq_num)
#plot(seq_num)


a = input$seq[1]
b = input$seq[2]
top_seq = reduced_evidence[reduced_evidence$Sequence %in% names(seq_num)[c(a:b)],]
ggplot(data = top_seq, aes(x=Sequence,y=Intensity,colour=Raw_file, fill = Charge)) +
  geom_boxplot(size = 0.75, alpha = 1)+ geom_point() +
  theme(text = element_text(size=25))
},height = plot_height_2))


```


RL {data-icon="fa-list"}
============================================
Column {data-width=600}
-----------------------------------------------------------------------

evidence[Retention_time > Retention_time_start & Retention_time < Retention_time_stop & Raw_file in file & Charge >= 2,]
```{r}


fillCol(height = plot_height_2,
renderPlot({
Retention_time_start = input$x_range[1]
Retention_time_stop = input$x_range[2]

evidence$Retention_Length = as.numeric(evidence$Retention_Length)
reduced_evidence = evidence[evidence$Retention_time > Retention_time_start & evidence$Retention_time < Retention_time_stop & evidence$Raw_file %in% input$file & evidence$Charge >= 2,]
sequences = reduced_evidence$Sequence
#length(sequences)

# arrange sequences with those found most often at the top
# sequences seem to be present multiple times per sample : need to work out why
seq_num = table(sequences)
head(seq_num)
seq_num = seq_num[rev(order(seq_num))]
head(seq_num)
#plot(seq_num)


a = input$seq[1]
b = input$seq[2]
top_seq = reduced_evidence[reduced_evidence$Sequence %in% names(seq_num)[c(a:b)],]
ggplot(data = top_seq, aes(x=Sequence,y=Retention_Length,colour=Raw_file)) +
  geom_boxplot(size = 0.75, alpha = 1)+ geom_point() +
  theme(text = element_text(size=25))
},height = plot_height_2))


```



RT {data-icon="fa-list"}
============================================
Column {data-width=600}
-----------------------------------------------------------------------

evidence[Retention_time > Retention_time_start & Retention_time < Retention_time_stop & Raw_file in file & Charge >= 2,]
```{r}


fillCol(height = plot_height_2,
renderPlot({
Retention_time_start = input$x_range[1]
Retention_time_stop = input$x_range[2]

evidence$Retention_time = as.numeric(evidence$Retention_time)
reduced_evidence = evidence[evidence$Retention_time > Retention_time_start & evidence$Retention_time < Retention_time_stop & evidence$Raw_file %in% input$file & evidence$Charge >= 2,]
sequences = reduced_evidence$Sequence
#length(sequences)

# arrange sequences with those found most often at the top
# sequences seem to be present multiple times per sample : need to work out why
seq_num = table(sequences)
head(seq_num)
seq_num = seq_num[rev(order(seq_num))]
head(seq_num)
#plot(seq_num)


a = input$seq[1]
b = input$seq[2]
top_seq = reduced_evidence[reduced_evidence$Sequence %in% names(seq_num)[c(a:b)],]
ggplot(data = top_seq, aes(x=Sequence,y=Retention_time,colour=Raw_file)) +
  geom_boxplot(size = 0.75, alpha = 1)+ geom_point() +
  theme(text = element_text(size=25))
},height = plot_height_2))


```



Charge {data-icon="fa-list"}
============================================
Column {data-width=600}
-----------------------------------------------------------------------

evidence[Retention_time > Retention_time_start & Retention_time < Retention_time_stop & Raw_file in file,]

```{r}



fillCol(height = plot_height_2,
renderPlot({
Retention_time_start = input$x_range[1]
Retention_time_stop = input$x_range[2]

reduced_evidence = evidence[evidence$Retention_time > Retention_time_start & evidence$Retention_time < Retention_time_stop & evidence$Raw_file %in% input$file,]
#sequences = reduced_evidence$Sequence
#length(sequences)

# arrange sequences with those found most often at the top
# sequences seem to be present multiple times per sample : need to work out why
#seq_num = table(sequences)
#head(seq_num)
#seq_num = seq_num[rev(order(seq_num))]
#head(seq_num)
#plot(seq_num)

ch_t = table(reduced_evidence[,c('Raw_file','Charge')])
ch_t = as.data.frame(ch_t)

#a = input$seq[1]
#b = input$seq[2]
#top_seq = reduced_evidence[reduced_evidence$Sequence %in% names(seq_num)[c(a:b)],]
ggplot(data = ch_t, aes(x=Raw_file,y=Freq,col=Raw_file,shape=Charge)) +
  geom_jitter(alpha = 0.75,size=10) +
  theme(text = element_text(size=25),axis.text.x=element_blank(),axis.ticks.x=element_blank())
},height = plot_height_2))


```


sd {data-icon="fa-list"}
============================================
Column {data-width=600}
-----------------------------------------------------------------------



```{r}


selectInput(inputId = 'c1',
            label = 'c1',
            choices = raw_list,
            selected = head(raw_list,3),
            multiple = TRUE)

selectInput(inputId = 'c2',
            label = 'c2',
            choices = raw_list,
            selected = tail(raw_list,3),
            multiple = TRUE)


ratio_function = function(seq_max,list_1,list_2){
  seq_names = colnames(seq_max)
  seq_ratios = seq_max[,0]
  #seq_ratios
  #rownames(seq_ratios)
  #head(seq_ratios)
  sd_list = c()
  for(i in list_1){
    #print(i)
    for(j in list_2){
      if(i != j){
        #print(paste(i,'/',j))
        ratio_name = paste(seq_names[i],'___',seq_names[j],sep='')
        #print(ratio_name)
        ratios = seq_max[i]/seq_max[j]
        seq_ratios[,ratio_name] = ratios
        #r = log2(as.numeric(as.matrix(ratios)))
        #r = r[is.finite(r)]
        #sd_list[ratio_name] = sd(r)
      }
    }
  }
  #head(seq_ratios)
  #d = density(log2(as.matrix(seq_ratios[,1])),na.rm=TRUE)
  #plot(d)
  #c2 = seq_ratios
  #df_sd = as.data.frame(sd_list)
  return(seq_ratios)
}

sd_ratio_function = function(ratio_df){
  sd_list = c()
  name_list = colnames(ratio_df)
  for(i in c(1:ncol(ratio_df))){
    r = log2(as.numeric(as.matrix(ratio_df[,i])))
    r = r[is.finite(r)]
    sd_list[name_list[i]] = sd(r)
  }
  return(as.data.frame(sd_list))
}

#  seq_evidence = evidence[,c("Raw_file","Sequence","Intensity")]
#  seq_evidence$Intensity = as.numeric(seq_evidence$Intensity)
#  
#  seq_max = cast(seq_evidence,Sequence~Raw_file, function(x) max(x,na.rm=TRUE))
# # 
# # 
#  do.call(data.frame,lapply(seq_max, function(x) replace(x, is.infinite(x),NA)))
#  rownames(seq_max) = seq_max[,1]
#  
#  seq_max[,1] = NULL

dim(seq_max)
#colnames(seq_max)
seq_names = colnames(seq_max)

con_1 = reactive({
  match(input$c1,seq_names)
})
renderText(con_1())

con_2 = reactive({
  match(input$c2,seq_names)
})
renderText(con_2())


c1 = reactive({
  ratio_function(seq_max,con_1(),con_1())
})

c1_stack = reactive({
  c1_stack = stack(log2(c1()))
  c1_stack$Condition = 'c1'
  c1_stack$Sequence = rownames(seq_max)
  c1_stack
})
  
c2 = reactive({
  ratio_function(seq_max,con_2(),con_2())
})

c2_stack = reactive({
  c2_stack = stack(log2(c2()))
  c2_stack$Condition = 'c2'
  c2_stack$Sequence = rownames(seq_max)
  c2_stack
})
  
c3 = reactive({
  ratio_function(seq_max,con_1(),con_2())
})

c3_stack =  reactive({
  c3_stack = stack(log2(c3()))
  c3_stack$Condition = 'c1_c2'
  c3_stack$Sequence = rownames(seq_max)
  c3_stack
})
  
seq_ratios = reactive({
  c_ratio_stack = rbind(c1_stack(),c2_stack(),c3_stack())
  colnames(c_ratio_stack) = c('log2_ratio','Raw_file','Condition','Sequence')
  c_ratio_stack$log2_ratio[!is.finite(c_ratio_stack$log2_ratio)] = NA 
  #head(c_ratio_stack)
  c_ratio_stack
})


fillCol(height = 300,
renderPlot({  
ggplot(seq_ratios(), aes(x=log2_ratio)) + geom_density(aes(group=Condition,col=Condition))
  
},height = 300))
  
df_sd_c1 = reactive({
  df_sd_c1 = sd_ratio_function(c1())
  df_sd_c1$Condition = 'c1'
  df_sd_c1
})

df_sd_c2 = reactive({
  df_sd_c2 = sd_ratio_function(c2())
  df_sd_c2$Condition = 'c2'
  df_sd_c2
})

df_sd_c3 = reactive({
  df_sd_c3 = sd_ratio_function(c3())
  df_sd_c3$Condition = 'c1_c2'
  df_sd_c3
})

c_sd = reactive({
  c_sd = rbind(df_sd_c1(),df_sd_c2(),df_sd_c3())
  colnames(c_sd) = c('standard_deviation','Condition')
  c_sd
})

fillCol(height = 300,
renderPlot({ 
  ggplot(c_sd(), aes(y=standard_deviation,x=Condition)) + geom_boxplot(aes(group=Condition,col=Condition))
},height = 300))
  
#   
# })







# 
# 
# condition_1 = c(3,4,5)
# condition_2 = c(8,9,10)
#
# c1 = ratio_function(seq_max,condition_1,condition_1)
# c1_stack = stack(log2(c1))
# c1_stack$Condition = 'c1'
# c1_stack$Sequence = rownames(seq_max)
# #head(c1_stack)
#
# c2 = ratio_function(seq_max,condition_2,condition_2)
# c2_stack = stack(log2(c2))
# c2_stack$Condition = 'c2'
# c2_stack$Sequence = rownames(seq_max)
# #head(c2_stack)
#
# c3 = ratio_function(seq_max,condition_1,condition_2)
# c3_stack = stack(log2(c3))
# c3_stack$Condition = 'c1_c2'
# c3_stack$Sequence = rownames(seq_max)
# #head(c3_stack)
#
# c_ratio_stack = rbind(c1_stack,c2_stack,c3_stack)
# colnames(c_ratio_stack) = c('log2_ratio','Raw_file','Condition','Sequence')
# c_ratio_stack$log2_ratio[!is.finite(c_ratio_stack$log2_ratio)] = NA
# #head(c_ratio_stack)
#
# ggplot(c_ratio_stack, aes(x=log2_ratio)) + geom_density(aes(group=Condition,col=Condition))
#
#
# df_sd_c1 = sd_ratio_function(c1)
# df_sd_c1$Condition = 'c1'
#
# df_sd_c2 = sd_ratio_function(c2)
# df_sd_c2$Condition = 'c2'
#
# df_sd_c3 = sd_ratio_function(c3)
# df_sd_c3$Condition = 'c1_c2'
#
# c_sd = rbind(df_sd_c1,df_sd_c2,df_sd_c3)
# colnames(c_sd) = c('standard_deviation','Condition')
#
# ggplot(c_sd, aes(y=standard_deviation,x=Condition)) + geom_boxplot(aes(group=Condition,col=Condition))
#
#
#

```

