---
title: "MaxQuant Reference Summary"
runtime: shiny
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(dplyr)
library(tidyr)
library(ggplot2)
library(leaflet)
library(DT)
load('/mnt/BLACKBURNLAB/QC/Reference/summary/QC.RData')
#dim(reduced_data)
#head(reduced_data)
#colnames(reduced_data)
date_order$Peaks.Repeatedly.Sequenced....
boxplot(date_order$Peaks.Repeatedly.Sequenced....)
colnames(date_order)[4:21]
colnames(date_order)

raw_list = unique(scans$Raw.file[2:length(scans$Raw.file)])

d=data.frame(date=(c("2014-02", '2014-03', "2014-09", "2016-03",'2016-11')), event=c("Dionex",'new QE',"Aeris", "Dual Column and Annual Service",'0'))



```

Column {.sidebar}
====================================================

In the panel RAW, current .raw files selected individually or in groups

```{r}

selectInput(inputId = 'file',
            label = 'Raw file',
            choices = raw_list,
            selected = raw_list,
            multiple = TRUE)
            
```


The slider allows you to move the start date forwards, in panels, 
MS and MS/MS,
Identified,
Peptides,
ppm,

```{r}


 sliderInput("integer", "Raw file Number", 
            min=0, max=length(date_order$date_collapse),
             value=c(500))
```




RAW {data-icon="fa-list"}
============================================
Current raw files are ovelayed upon ideal raw files


```{r}


scans$Total.ion.current = signif(scans$Total.ion.current,3)
 sliderInput("y_range", "TIC Range", 
             min=1e6, max=1.2e10,
             value=c(0,5e9),
             dragRange = T,
             width = 800)

raw_list = unique(scans$Raw.file[2:length(scans$Raw.file)])

#selectInput(inputId = 'RAW',
#            label = 'RAW file',
#            choices = raw_list)

 sliderInput("x_range", "Retention Time Range", 
             min=0, max=max(scans$Retention.time,na.rm=TRUE),
             value=c(0,max(scans$Retention.time,na.rm= TRUE)),
             step = 1,
             dragRange = T,
             width = 800)


fillCol(height = 500,
renderPlot({
ggplot(data = ideal_scans, aes(x=Retention.time,y=Total.ion.current,colour=Raw.file)) +
    geom_line(size = 0.08, alpha = 1) +
    ylim(input$y_range[1],input$y_range[2]) +
    xlim(input$x_range[1],input$x_range[2]) +
    #geom_line(data = scans[scans$Raw.file %in% #raw_list[input$file_range[1]:input$file_range[2]],],
    geom_line(data = scans[scans$Raw.file %in% input$file,],
      aes(x=Retention.time,y=Total.ion.current,colour=Raw.file),size = 0.1)
},height = 500))



```

MS and MS/MS {data-icon="fa-list"}
============================================
Column {data-width=650}
-----------------------------------------------------------------------

### MS

```{r}

fillCol(height = 300,
renderPlot({
  #q <- qplot(date_collapse,',column_name,',data=reduced_data,geom=c("boxplot","point"),colour = column_volume)
  ggplot(date_order[c(input$integer:length(date_order$date_collapse)),],
       aes(date_collapse, MS)) + 
  geom_boxplot(aes(colour = column_volume)) +
  theme(text = element_text(size=15),axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(x = NULL, y = NULL)
},height = 300))

```

### MS/MS

```{r}

fillCol(height = 300,
renderPlot({
  print(input$integer)
  #q <- qplot(date_collapse,',column_name,',data=reduced_data,geom=c("boxplot","point"),colour = column_volume)
  ggplot(date_order[c(input$integer:length(date_order$date_collapse)),],
       aes(date_collapse, MS.MS)) + 
  geom_boxplot(aes(colour = column_volume)) +
  theme(text = element_text(size=15),axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(x = NULL, y = NULL)
},height = 300))
```



Identified {data-icon="fa-list"}
============================================
Column {data-width=350}
-----------------------------------------------------------------------

### log2(MS/MS / MS)

```{r}

fillCol(height = 300,
renderPlot({
  #q <- qplot(date_collapse,',column_name,',data=reduced_data,geom=c("boxplot","point"),colour = column_volume)
  date_order$MS2per = log2(date_order$MS.MS/date_order$MS)
  ggplot(date_order[c(input$integer:length(date_order$date_collapse)),],
       aes(date_collapse, MS2per)) + 
  geom_boxplot(aes(colour = column_volume)) +
    theme(text = element_text(size=15),axis.text.x = element_text(angle = 90, hjust = 1)) +
    scale_y_continuous(limits = c(0,2)) +
    labs(x = NULL, y = NULL)
  
},height = 300))

```

### MS.MS.Identified....

```{r}
fillCol(height = 300,
renderPlot({
  #q <- qplot(date_collapse,',column_name,',data=reduced_data,geom=c("boxplot","point"),colour = column_volume)
  ggplot(date_order[c(input$integer:length(date_order$date_collapse)),],
       aes(date_collapse, MS.MS.Identified....)) + 
  geom_boxplot(aes(colour = column_volume)) +
    theme(text = element_text(size=15),axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(x = NULL, y = NULL)
},height = 300))
```



Peptides {data-icon="fa-list"}
============================================
Column {data-width=350}
-----------------------------------------------------------------------

### Peptide.Sequences.Identified

```{r}

fillCol(height = 300,
renderPlot({
  #q <- qplot(date_collapse,',column_name,',data=reduced_data,geom=c("boxplot","point"),colour = column_volume)
  ggplot(date_order[c(input$integer:length(date_order$date_collapse)),],
       aes(date_collapse, Peptide.Sequences.Identified)) + 
  geom_boxplot(aes(colour = column_volume)) +
    theme(text = element_text(size=15),axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(x = NULL, y = NULL)+
    #xlim(date_collapse[1],date_collapse[100])+
#xlim(date_order[input$integer,date_collapse],date_order[length(date_order$date_collapse),date_collapse])+
    geom_vline(data=d, mapping=aes(xintercept=date), color="blue") +
geom_text(data=d, mapping=aes(x=date, y=0, label=event), size=4, angle=90, vjust=-0.4, hjust=0)
    

},height = 300))

```

### Peaks.Repeatedly.Sequenced....

```{r}
fillCol(height = 300,
renderPlot({
  #q <- qplot(date_collapse,',column_name,',data=reduced_data,geom=c("boxplot","point"),colour = column_volume)
  ggplot(date_order[c(input$integer:length(date_order$date_collapse)),],
       aes(date_collapse, Peaks.Repeatedly.Sequenced....)) + 
  geom_boxplot(aes(colour = column_volume)) +
    theme(text = element_text(size=15),axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(x = NULL, y = NULL)
},height = 300))
```


ppm {data-icon="fa-list"}
============================================
Column {data-width=350}
-----------------------------------------------------------------------

### Av..Absolute.Mass.Deviation..ppm.

```{r}

fillCol(height = 300,
renderPlot({
  #q <- qplot(date_collapse,',column_name,',data=reduced_data,geom=c("boxplot","point"),colour = column_volume)
  ggplot(date_order[c(input$integer:length(date_order$date_collapse)),],
       aes(date_collapse, Av..Absolute.Mass.Deviation..ppm.)) + 
  geom_boxplot(aes(colour = column_volume)) +
    theme(text = element_text(size=15),axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(x = NULL, y = NULL)
},height = 300))

```

### Mass.Standard.Deviation..ppm.

```{r}
fillCol(height = 300,
renderPlot({
  #q <- qplot(date_collapse,',column_name,',data=reduced_data,geom=c("boxplot","point"),colour = column_volume)
  ggplot(date_order[c(input$integer:length(date_order$date_collapse)),],
       aes(date_collapse, Mass.Standard.Deviation..ppm.)) + 
  geom_boxplot(aes(colour = column_volume)) +
    theme(text = element_text(size=15),axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(x = NULL, y = NULL)
},height = 300))
```





Other {data-icon="fa-list"}
============================================

### Select the column to visualise 


```{r}

selectInput(inputId = 'data_column',
            label = 'Choose summary column',
            choices = colnames(date_order)[4:14])

 sliderInput("range", "Date Range", 
             min=0, max=length(date_order$date_collapse),
             value=c(length(date_order$extracted_date)-150,length(date_order$extracted_date)),
             dragRange = T,
             width = 800)
 
  # sliderInput("date_range", "Date Range",
  #             min=as.Date(date_order$extracted_date[0]),
  #             max=as.Date(date_order$extracted_date[length(date_order$date_collapse)]),
  #             value = as.Date(date_order$extracted_date[0]),
  #             timeFormat = '%y-%m-%d',
  #             timezone = F)
  # 
 selected_df <- reactive({
  subset_df <- date_order[,c(
                                    which(colnames(date_order) == 'extracted_date'),
                                    which(colnames(date_order) == input$data_column),
                                    which(colnames(date_order) == 'column_volume')
                                    )]
  colnames(subset_df) <- c('date','property','column_volume')
  subset_df
 })
 


            #selected = 'Peptide.Sequences.Identified')

fillCol(height = 500,
renderPlot({
  #q <- qplot(date_collapse,',column_name,',data=reduced_data,geom=c("boxplot","point"),colour = column_volume)
  ggplot(selected_df()[c(input$range[1]:input$range[2]),],
       aes(date, property)) + 
  geom_boxplot(aes(colour = column_volume)) +
    theme(text = element_text(size=15),axis.text.x = element_text(angle = 90, hjust = 1)) +
    labs(x = NULL, y = NULL)

},height = 500))
```





